Teacher Beauty Affects Their Ratings More Than We Think

### 2023-04-18 outputs/paper/paper.qmd
data download plus cleaning up

@@

>>>>

# could try to do something with like male vs female evaluation and also  eval

# minority vs non minority and their average eval

#age and evaluation

# native vs non native and eval 
```

```{r}
#| echo: false
#| message: false
library(dplyr)
library(ggplot2)

# male vs female evaluation 
males <- subset(TeachingRatings, gender == "male") |> select(eval, beauty, gender)
average_male_eval <- mean(males$eval)
average_male_beauty <- mean(males$beauty)

plot(eval ~ beauty, data = males)

females <- subset(TeachingRatings, gender == "female") |> select(eval, beauty, gender)
average_female_eval <- mean(females$eval)
average_female_beauty <- mean(females$beauty)
plot(eval ~ beauty, data = females)

# would be cool to do like a male vs females like two lines on one graph and they like show beauty vs. eval

@@

```{r}
#| echo: false
#| message: false
# age vs evaluation 
age_vs_eval_beauty <- select(age, beauty, eval)
```
